% A simple CV example
% Copyright (C) 2020-2021 hnqiu. All Rights Reserved.
% Licensed under the MIT License. See LICENSE for details.

% Project is hosted at
% https://github.com/hnqiu/simplecv


\documentclass{simplecv}
\usepackage[utf8]{inputenc}
\usepackage[margin=2cm]{geometry}


\setfooter{Updated in Jun 2021}

% personal information in this document is IMAGINARY

\begin{document}

\name{hnqiu}
\personalinfo{42 XXX Street}{City}{1024}
             {email@domain.com}{0123 456 789}


\cvsection{Profile}
\cvitem{PhD candidate in intelligent robotic control}
\cvitem{Active programmer in computational intelligence and machine learning}



\cvsection{Education}
\cvevent{2017/03--present}{PhD in Electrical Engineering}
        {Wild Rooster University}{City, Country}
\cvitem{Topic?}
\cvsubitem{I work on something}
\cvsubitem{I work on something else}

\cvevent{2009/09--2013/06}{B.S. in Electrical Engineering}
        {Jialidun University}{City, Country}
\cvitem{GPA: 4.01/4.0}



\cvsection{Work}

\cvevent{2015/07--2017/03}{Embedded System Design}
        {Company}{City, Country}
\cvitem{Circuit design and C programming}
\cvitem{Algorithm implementation on microprocessors}




\cvsection{IT Skills}

\cvskill{C++}{9}
\cvskill{Python}{7}
\cvskill{MATLAB \& Simulink}{9}
\cvskill{Robot Operating System (ROS)}{8}
\cvskill{Git}{8}
\cvskill{Latex}{9}



\cvsection{Publications}

\cvitem{
\textbf{hnqiu}, San Zhang.
\newblock Towards a rooster that lays eggs.
\newblock In {\em Proceedings of the 2020 Artificial Intelligence
  Conference}, Jun 2020, pp. 10--18.
}

\cvitem{
\textbf{hnqiu}, Si Li.
\newblock How to Jialidun: a comprehensive study.
\newblock In {\em 2018 International Conference on Computational Intelligence},
  Dec 2018, pp. 1--10.
}



\cvsection{Languages}

\cvlangitem{Mandarin \& Cantonese (native)}{English (fluent)}



\cvsection{Referee}

\cvreferee{Dr. San Zhang}{Professor}
          {School of Engineering, Wild Rooster University}
          {san.zhang@wru.edu}
          {0123 456 789}
          {https://wildroosteruniversity/people/zhang-san}

\end{document}
